Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-26 1-Main.tex
Updates from Overleaf

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

    \author{Jean-Christophe Bach}
    \address{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}
    % \ead{firstname.lastname@imt-atlantique.fr}

@@

    \abstract{\input{2-Abstract}}
    \keywords{Multilevel Modeling Challenge, Federation Modeling Language, OpenFlexo}
    \bibliography{biblio.bib}
}

@@

\noteSM{test}
\noteJC{test}
\noteSylvain{test}
\noteAntoine{test}
\noteFabien{test}
\noteJoel{test}

@@

\section{Conclusions}
\input{10-Conclusions.tex}

>>>>

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    %numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

    \author{Jean-Christophe Bach}
    \address{IMT Atlantique, Lab-STICC, UMR 6285, 29238 Brest, France}
    % \ead{firstname.lastname@imt-atlantique.fr}

@@

    \abstract{\input{2-Abstract}}
    \keywords{Multilevel Modeling Challenge, Federation Modeling Language, Openflexo}
    \bibliography{biblio.bib}
}

@@

%\noteSM{test}
%\noteJC{test}
%\noteSylvain{test}
%\noteAntoine{test}
%\noteFabien{test}
%\noteJoel{test}

@@

\section{Conclusions}
\label{sec:conclusions}
\input{10-Conclusions.tex}

### 2021-05-26 6-ModelPresentation.tex

% detailed  presentation of a model, including justifications for design decisions

@@

\begin{lstlisting}[breaklines=true, language=java, basicstyle=\ttfamily\scriptsize, mathescape=true]
concept ActorType extends Type {
 ActorType[0..*] parentActorTypes;
 ...
 boolean isOrSpecializes(ActorType actorType) {    
  if (actorType = this)   
   return true;      
  for (p : parentActorTypes) {      
   if (p.isOrSpecializes(actorType)
    return true;        
  return false;    
 }
 ...
}

>>>>

%Model Presentation: detailed  presentation of a model, including justifications for design decisions

\todo[inline]{phrase d'intro pour expliquer que les req étaient couverts au fur et à mesure (côté systématique)}

@@

\begin{lstlisting}[breaklines=true, language=java, basicstyle=\ttfamily\scriptsize, mathescape=true]
concept ActorType extends Type {
 ActorType[0..*] parentActorTypes;
 ...
 boolean isOrSpecializes(ActorType actorType) {    
  if (actorType == this)   
   return true;      
  for (p : parentActorTypes) {      
   if (p.isOrSpecializes(actorType)
    return true;        
  return false;    
 }
 ...
}
